### 2022-02-08 README.Rmd
update binder to work with renv

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/yichun33/archyconfgender/master?urlpath=rstudio)
[![.github/workflows/knit-in-Docker.yaml](https://github.com/yichun33/archyconfgender/actions/workflows/knit-in-Docker.yaml/badge.svg)](https://github.com/yichun33/archyconfgender/actions/workflows/knit-in-Docker.yaml)
